---
title: "Simple document"
output: github_document
---

```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(readxl)
library(haven)
```

## Import some data

I want to import `FAS_litters.csv`. 

```{r message=FALSE, warning=FALSE}
litters_df = read_csv("data/FAS_litters.csv")
```

Yay! I imported the dataset. Now I want better names.

```{r}

litters_df = janitor::clean_names(litters_df)

names(litters_df)
```

Yay! Now I have better names. Let's look at the dataset.

```{r}
litters_df

head(litters_df)
tail(litters_df)
```

One I use a lot is:

```{r, eval=FALSE}
View(litters_df)
```

Here's `skimr`:
```{r}
skimr::skim(litters_df)
```

## Arguments in `read_csv`

Note that in class we reviewed the various arguments read_csv could take, e.g. skip, na, etc. Review these!

Let's try specifying column types:

```{r}
litters_data = read_csv(file = "Data/FAS_litters.csv",
  col_types = cols(
    Group = col_character(),
    `Litter Number` = col_character(),
    `GD0 weight` = col_double(),
    `GD18 weight` = col_double(),
    `GD of Birth` = col_integer(),
    `Pups born alive` = col_integer(),
    `Pups dead @ birth` = col_integer(),
    `Pups survive` = col_integer()
  )
)
tail(litters_data)
```

## Reading from excel

```{r}
mlb11_df = read_excel("Data/mlb11.xlsx")
mlb11_df
```

LOTR words is next. We can control how much of the excel we read in using 'range.'

```{r}
fellow_df = read_excel("Data/LotR_Words.xlsx", range = "B3:D6")
fellow_df
```

## Read a SAS file

You can read in from SAS, Stata, SPSS, and a number of other filetypes. Suppose we want to read in a SAS file. The below doesn't work, but we're trying!

```{r, eval=FALSE}
pulse_df = read_sas("Data/public_pulse_data.sas7bdat")
```